Multi-channel Kondo model URG

### 2021-12-14 notes/mck_urg.tex
added bath free energy non-analyticity

\section{Bath Susceptibility from zero-mode fixed point Hamiltonian}
We insert a magnetic field that acts only on the bath and then attempt to diagonalize the Hamiltonian.
\begin{align}
	H(h) = J^* \vec{S_d}\cdot\vec{s}_\text{tot} + h s^z_\text{tot}
\end{align}

@@

	\lambda_{m, \pm}^{M, h} &= -\frac{J}{4} + (2m+1)h/2 \pm \frac{1}{2}\sqrt{J^2x^M_m + \left[(2m+1)h - \frac{J}{2}\right]^2 - 4m(m+1)(h^2 - J^2/4)} \\
				&= -\frac{J}{4} + (2m+1)h/2 \pm \frac{1}{2}\sqrt{J^2(M + \frac{1}{2})^2 + h^2 - (2m+1)Jh}	= -\frac{J}{4} + (2m+1)h/2 \pm \phi^M_m

@@

@@

>>>>

\section{Bath Susceptibility from zero-mode fixed point Hamiltonian}
We insert a magnetic field that acts only on the bath and then attempt to diagonalize the Hamiltonian.
\begin{align}
	\label{bath_field_ham}
	H(h) = J^* \vec{S_d}\cdot\vec{s}_\text{tot} + h s^z_\text{tot}
\end{align}

@@

	\lambda_{m, \pm}^{M, h} &= -\frac{J}{4} + (2m+1)h/2 \pm \frac{1}{2}\sqrt{J^2x^M_m + \left[(2m+1)h - \frac{J}{2}\right]^2 - 4m(m+1)(h^2 - J^2/4)} \nonumber\\
				&= -\frac{J}{4} + (2m+1)h/2 \pm \frac{1}{2}\sqrt{J^2(M + \frac{1}{2})^2 + h^2 - (2m+1)Jh} \nonumber\\
				&= -\frac{J}{4} + (2m+1)h/2 \pm \phi^M_m \label{bath_field_ens}

@@

where \(\phi^M_m = \frac{1}{2}\sqrt{J^2(M + \frac{1}{2})^2 + h^2 - (2m+1)Jh}\).

@@

\subsection{Field coupled to bath zero modes}
Assuming a non-degenerate ground state for \(h \neq 0\), the zero temperature free energy becomes
\begin{equation}\begin{aligned}
	F(h\neq 0, T\to 0) = -\frac{1}{\beta}\ln e^{-\beta E_\text{min}} = E_\text{min}
\end{aligned}\end{equation}
In the star graph Hamiltonian with \(K-\)channels and in the presence of a field on the bath zero modes (eq.~\ref{bath_field_ham}), the energy eigenvalues for a particular value of \(s_\text{tot}\) are given in eq.~\ref{bath_field_ens}. For small field \(h\), the global ground state will lie in the subspace of \(s_\text{tot} = M_\text{max} = K/2\). The ground state energy will be one of the negative eigenvalues:
\begin{equation}\begin{aligned}
	\lambda^{M_\text{max},h}_{m, -} = -J/4 + \left( 2m+1 \right)\frac{h}{2} - \frac{1}{2}\sqrt{J^2(M_\text{max}+\frac{1}{2})^2 + h^2 - \left( 2m+1 \right) Jh}
\end{aligned}\end{equation}
The minimum eigenvalue is obtained by minimizing \(h(2m+1)\). For \(h>0\), the ground state is realized for the most negative value of \(m\), \(-M_\text{max}\). On the other hand, for \(h<0\), it occurs for \(m=M_\text{max}-1\), because that is the most positive value it can take. Therefore, the minimal energy eigenvalue is
\begin{equation}\begin{aligned}
	E_\text{min}(h) = \begin{cases}
		-J/4 - \frac{h}{2}\left(K-1\right) - \frac{1}{2}\sqrt{\frac{1}{4}J^2(K+1)^2 + h^2 + \left(K-1\right) Jh}, & h>0\\
		-J/4 + \frac{h}{2}\left(K-1\right) - \frac{1}{2}\sqrt{\frac{1}{4}J^2(K+1)^2 + h^2 - \left(K-1\right) Jh}, & h<0\\
	\end{cases}
\end{aligned}\end{equation}
The free energy for a non-zero field is therefore
\begin{equation}\begin{aligned}
	F(h\neq 0, T\to 0) = -J/4 - \frac{|h|}{2}\left(K-1\right) - \frac{1}{4}\sqrt{J^2(K+1)^2 + 4h^2 + 4\left(K-1\right) J |h|}
\end{aligned}\end{equation}
The first derivative of the free energy with respect to the field gives
\begin{equation}\begin{aligned}
	F^\prime(h\neq 0, T\to 0) = - \frac{1}{2}(K-1)\text{sign}(h) - \frac{h + \frac{1}{2}J(K-1)\text{sign}(h)}{\sqrt{J^2(K+1)^2 + 4h^2 + 4\left(K-1\right) J |h|}}
\end{aligned}\end{equation}
There we used the result that the derivative of \(|x|\) is \(\text{sign}(x)\). If we now take \(h\) to zero from both directions, we get
\begin{equation}\begin{aligned}
	F^\prime(h \to 0^\pm, T\to 0) = \mp \frac{1}{2}\frac{(K-1)(K+2)}{K+1}
\end{aligned}\end{equation}
The first derivative of the free energy is therefore discontinuous as the field coupled to the bath \(h\to 0\); it goes to different values depending on the direction in which we take the limit. The only case where it is not analytic is when \(K=1\); then the derivative goes to zero from both directions. This non-analyticity has also been verified numerically.
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.6\textwidth]{../numerics/disc_mag_bath.pdf}
	\caption{Non-analytic free energy for \(K>1\) and analytic free energy for \(K=1\).}
\end{figure}
